---
title: "Life_Expectancy_with_suicideRate"
output:
  html_notebook: default
  pdf_document: default
---

### Load libraries
 

```{r}
library(dplyr)
library(tidyr)
library(tidyverse)
library(ggplot2)
library(stringr)
```

### Importing the dataset

```{r}
life_ex <- read.csv("C:\\Users\\Pc World Computers\\OneDrive\\Desktop\\Downloads\\Life expectancy.csv")
suicide_rate <- read.csv("C:\\Users\\Pc World Computers\\OneDrive\\Desktop\\Downloads\\Suicide Rate.csv")

```



### Combine these datasets with "Country" using merge function

```{r}
life_df <- merge(life_ex,suicide_rate, by="Country")
view(head(life_df))
```

### Columns in the dataset

```{r}
colnames(life_df)
```

### Rename the columns 

```{r}
life_df <- life_df %>%
         rename("country"="Country",
                "men_life_expectancy"="Life.Expectancy..years....Men",
                "women_life_expectancy"="Life.Expectancy..years....Women",
                "happiness_score"="Happiness.Score",
               "women_fertility_rate" ="Fertility.Rate..births.per.woman.",
               "gdp_per_capita"="GDP.per.capita",
               "suicide_rate"="Suicide.rate"
                )
view(head(life_df))
```

### Check null values in dataset

```{r}
colSums(is.na(life_df))
```
### Qno1 - Top 5 countries with men highest life expectancy rate?
```{r}
top5_men <- life_df %>%
          select(country,men_life_expectancy)%>%
          filter(men_life_expectancy != 0)%>%
          arrange(desc(men_life_expectancy))
top5_men = head(top5_men,5)
top5_men

```
###  Qno2 - Top 5 countries with women highest life expectancy rate?

```{r}
top5_women <- life_df %>%
          select(country,women_life_expectancy)%>%
          filter(women_life_expectancy != 0)%>%
          arrange(desc(women_life_expectancy))
top5_women = head(top5_women,5)
top5_women

```
###  Qno3 - Top 5 countries with the highest suicide rate and happiness score?

```{r}
top5_happiness_suicide <- life_df %>%
          select(country,happiness_score,suicide_rate)%>%
          filter(happiness_score & suicide_rate != 0)%>%
          arrange(desc(happiness_score),desc(suicide_rate))

head(top5_happiness_suicide,5)

```
### Qno4- Top 5 countries with the highest suicide rate and highest gdp?

```{r}
top5_suicide_gdp <- life_df %>%
                select(country,suicide_rate,gdp_per_capita,men_life_expectancy,women_life_expectancy) %>%
                arrange(desc(suicide_rate),gdp_per_capita)

head(top5_suicide_gdp,5)
```

